Fixing Vulnerabilities Hinders Maintainability

### 2020-02-06 paper/icpc20.tex

Security is a requirement of utmost importance to produce software with 
high quality. However, there is still a considerable amount of 
vulnerabilities being discovered and fixed, almost weekly. We suspect 
that when developers address these vulnerabilities on their codebases, 
they actually affect the maintainability of software, potentially 
introducing other vulnerabilities. This paper evaluates the impact of 
patches to improve security on the maintainability of open-source software. 
Maintainability is measured based on the Better Code Hub’s model of $10$ 
guidelines using a dataset including $1037$ security commits. Results show 
that fixing software vulnerabilities hinders the maintainability of 
open-source software. This is particularly the case for patches that address Path Traversal (CWE-22),
Information Exposure (CWE-200) and Resource Management Errors (CWE-399) . We conclude that changes to code bases 
to fix vulnerabilities need to be performed with extra care and that security-related code evolution should be subject in computer curricula.

@@

exploit their resources. As an example, in the last week of January $2019$, 

@@

were empirically validated in previous work~\cite{Bijlsma:2012:FIR:2317098.2317124, 8530041}. 

@@

Especially, for patches that address \emph{Broken Authentication and Session Management} 
issues, \emph{Memory Leaks} and \emph{Denial-of-Service} attacks. This is important work

@@

PHP interpreter\footnote{\label{openssl}OpenSSL is a toolkit that

>>>>

Security is a requirement of utmost importance to produce software with 
high quality. However, there is still a considerable amount of 
vulnerabilities being discovered and fixed, almost weekly. We suspect 
that when developers address these vulnerabilities on their codebases, 
they actually affect the maintainability of software, potentially 
introducing other vulnerabilities. This paper evaluates the impact of 
patches to improve security on the maintainability of open-source software. 
Maintainability is measured based on the Better Code Hub’s model of $10$ 
guidelines using a dataset including $1037$ security commits. Results show 
that fixing software vulnerabilities hinders the maintainability of 
open-source software. This is particularly the case for patches that address Path Traversal (CWE-22),
Information Exposure (CWE-200) and Resource Management Errors (CWE-399). We conclude that changes to code bases 
to fix vulnerabilities need to be performed with extra care and that security-related code evolution should be subject in computer curricula.

@@

exploit their resources. \Sof{Improve example - outdated}As an example, in the last week of January $2019$, 

@@

were empirically validated in previous work~\cite{Bijlsma:2012:FIR:2317098.2317124, 8530041, cruz2019energyoriented}. 

@@

Especially, for patches that address Path Traversal (CWE-22),
Information Exposure (CWE-200) and Resource Management Errors (CWE-399). This is important work

@@

protocol implementation of OpenSSL\footnote{\label{openssl}OpenSSL is a toolkit that
